\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage{url}
\usepackage[square,sort,numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}

\newcommand{\myurl}[1]{\href{#1}{#1}}

\setlength\parindent{0pt}

\title{Pedro Ribeiro Mendes J{\'u}nior}
\author{University of Campinas\\Institute of Computing}

\newcommand{\mycite}[1]{\citeauthor{#1}~\cite{#1}}

\begin{document}

\nocite{Penatti2015}
\nocite{Pazinato2015}
% \nocite{MendesJr2014}
\nocite{MendesJunior2011}

\maketitle

CV: \myurl{http://lattes.cnpq.br/4535492803722330} (in portuguese)

% For references, see the following BibTeX file: \myurl{https://github.com/pedrormjunior/pedrormjunior.github.io/blob/master/pedrormjunior.bib}

\section*{Important material}
\label{sec:important-material}

Algorithms used in the work \ref{ref:MendesJunior2011}: \myurl{https://github.com/pedrormjunior/vlpl}.

Datasets used in the work \ref{ref:MendesJunior2011}: \myurl{https://github.com/pedrormjunior/vlpl/blob/master/imgs-database}.

\section*{Publications}

\subsection*{Journal articles}

\begin{enumerate}[label={[\arabic*]}]
\item\label{ref:Pazinato2016} Pazinato, Daniel; Stein, Bernardo; de Almeida, Waldir; Werneck, Rafael; \textbf{Mendes Júnior, Pedro}; Penatti, Otávio; Torres, Ricardo; Menezes, Fabio; Rocha, Anderson (2016), ``\href{http://dx.doi.org/10.1109/JBHI.2014.2386796}{Pixel-Level Tissue Classification for Ultrasound Images}'', \emph{IEEE Journal of Biomedical and Health Informatics}. 20(1):256--267.
\item\label{ref:Penatti2015} Penatti, Otávio; Werneck, Rafael; de Almeida, Waldir; Stein, Bernardo; Pazinato, Daniel; \textbf{Mendes Júnior, Pedro}; Torres, Ricardo; Rocha, Anderson (2015), ``\href{http://dx.doi.org/10.1016/j.compbiomed.2015.08.004}{Mid-level Image Representations for Real-time Heart View Plane Classification of Echocardiograms}'', \emph{Computers in Biology and Medicine}. 66:66--81.
\end{enumerate}

\subsection*{Proceedings}

\begin{enumerate}[label={[\arabic*]},resume]
\item\label{ref:Li2015} Li, Lin; Muñoz, Javier; Almeida, Jurandy; Calumby, Rodrigo; Penatti, Otávio; Dourado, Ícaro; Nogueira, Keiller; \textbf{Mendes Júnior, Pedro}; Pereira, Luís; Pedronette, Daniel; dos Santos, Jefersson; Gonçalvez, Marcos; Torres, Ricardo (2015), ``\href{http://ceur-ws.org/Vol-1436/Paper49.pdf}{RECOD @ Placing Task of MediaEval 2015}'', In: \emph{MediaEval 2015 Workshop}. pp. 1--3.
\item\label{ref:Li2014} Li, Lin; Penatti, Otávio; Almeida, Jurandy; Chiachia, Giovani; Calumby, Rodrigo; \textbf{Mendes Júnior, Pedro}; Pedronette, Daniel; Torres, Ricardo (2014), ``\href{http://ceur-ws.org/Vol-1263/mediaeval2014_submission_81.pdf}{Multimedia geocoding: The RECOD 2014 approach}'', In: \emph{MediaEval 2014 Workshop}. pp. 1--2.
\item\label{ref:MendesJunior2011} \textbf{Mendes Júnior, Pedro}; Neves, José Maria; Taveres, Andrea; Menotti, David (2011), ``\href{http://dx.doi.org/10.1109/icsmc.2011.6084108}{Towards an automatic vehicle access control system: License plate location}'', In: \emph{IEEE Intl. Conference on Systems, Man, and Cybernetics (SMC)}. pp. 2916--2921.
\item\label{ref:MendesJunior2010} \textbf{Mendes Júnior, Pedro}; Neves, José Maria; Menotti, David (2010), ``Em rumo a um sistema automático de controle de acesso de veículos automotivos: Localização de placas de identificação'', In: \emph{WUW Workshop of Undergraduate Work -- XXIII Conference on Graphics, Patterns and Image (SIBGRAPI)}.
\end{enumerate}

\subsection*{Patents}

\begin{enumerate}[label={[\arabic*]},resume]
\item\label{ref:MendesJunior2014a} \textbf{Mendes Júnior, Pedro}; Souza, Roberto; Werneck, Rafael; Stein, Bernardo; Pazinato, Daniel; de Almeida, Waldir; Penatti, Otávio; Torres, Ricardo; Rocha, Anderson (2014), ``Method for Multiclass Classification in Open-set Scenarios and uses thereof'', \emph{United States Patent and Trademark Office (USPTO)}. U.S. Patent: 14532580. Filing date:  11/04/2014.\\
\item\label{ref:MendesJunior2014} \textbf{Mendes Júnior, Pedro}; Souza, Roberto; Werneck, Rafael; Stein, Bernardo; Pazinato, Daniel; de Almeida, Waldir; Penatti, Otávio; Torres, Ricardo; Rocha, Anderson (2014), ``Método para classificação multiclasse em cenários abertos e usos do mesmo'', \emph{Instituto Nacional da Propriedade Industrial (INPI)}. Brazil: BR10201402378. Filing date: 09/25/2014.\\
\item\label{ref:Rocha2014} Rocha, Anderson; Torres, Ricardo; Penatti, Otávio; \textbf{Mendes Júnior, Pedro}; Pazinato, Daniel; de Almeida, Waldir; Werneck, Rafael; Stein, Bernardo (2014), ``Método para classificação automática de visões do coração a partir de ecocardiogramas'', \emph{Instituto Nacional da Propriedade Industrial (INPI)}. Brazil: BR10201401105. Filing date: 05/07/2014.
\end{enumerate}

% \bibliography{pedrormjunior}
% \bibliographystyle{unsrtnat}

\end{document}